%-----------------------------------------------------------------------------%
% Letter class
\documentclass[11pt]{letter}
\usepackage{hyperref}
\usepackage[backend=bibtex,style=verbose,doi=false,isbn=false,url=false]{biblatex}
% \addbibresource{phd-bibliography/pollen-competition.bib}
\usepackage{geometry}
\geometry{textwidth=43em, textheight=52\baselineskip}
% Name of sender
\name{Alba Cervantes Loreto}
% Signature of sender
\signature{Alba Cervantes Loreto}
% Address of sender
\address
{
Alba Cervantes Loreto \\
 School of Biological Sciences\\
University of Canterbury, Christchurch 8140, New Zealand\\
albaricoque.cl.93@gmail.com\\
+64~22~508~6030
}
\date{19--Aug--2021}
%-----------------------------------------------------------------------------%
\begin{document}


% Name and address of receiver
\begin{letter}
{



Environment Canterbury,\\
Regional Council\\
Christchurch, New Zealand\\

}
% Opening statement
\opening{Dear Principal Advisor-Biosecurity, }
% Letter body
I am writing to apply for the Biosecurity Advisor- Invasive Organisms position within Environment Canterbury. I am in the final stages of my Ph.D. at the University of Canterbury, which is focused on analyzing ecological questions about species interactions using statistical and computational tools.  My expected submission date is in October 2021.


I am an ecologist, specialized in terrestrial environments with more than 5 years of experience working in research. I have worked in a diverse array of terrestrial systems and species, such as native grasslands, managed agroecosystems, annual plant communities, and pollinated systems. I have extensive experience designing and implementing experiments, plant taxonomy and identification, field surveys to monitor ecological systems, and data collection. My years involved in science collaborations have cultivated my skills to perform reproducible and replicable analyses and to understand the importance of communicating the findings with clarity and precision. I believe I am an excellent candidate for this position because I have both the scientific background and the technical skills to assess and mitigate the risk associated with invasive species in the Canterbury Region.
%I have a solid understanding of the biotic and abiotic factors that shape the structure and functioning of ecological communities.
 %I have a solid understanding of frequentist and bayesian statistical methods, as well as data wrangling in a variety of programming languages



My skills are not only limited to the analytical aspect of science. I have a strong understanding of the importance of collaborative work and I have the proven ability to communicate complex findings in a variety of ways such as scientific papers, technical reports, and oral presentations. Furthermore, my teaching experience has proven my ability to guide and educate people in the process of analyzing data, which is an aspect of my career that I have particularly enjoyed. I have been part of many collaborations with different groups, and I genuinely enjoy working in a team. I also firmly believe the best outcomes are achieved when people within different disciplines work together. I am convinced that my excellent interpersonal skills will allow me to adapt and positively contribute to the different teams across Environment Canterbury.




After years in academia, I am ready for a change. I have decided to pursue my passion for public service and conservation to contribute my gained skills, experience, and commitment to the country that I now call home, Aotearoa New Zealand. Environment Canterbury offers an exciting opportunity to do so, as it is an interdisciplinary agency focused on improving the way the environment is managed. Invasive species represent a prooven threat to diversity maintenance and ecosystem services. Managing them is crucial to have a healthy environment that all New Zealand residents benefit from. I believe Environment Canterbury shares that vision. I feel equipped to respond to the challenges offered by this position, please let me know if I can provide additional information to aid you in the evaluation of my application. Thank you for considering my application, and I look forward to hearing from you.
\vfill

\hfill
Alba Cervantes Loreto

\medskip
% Closing statement
% \closing{ }
\end{letter}
\end{document}
%-----------------------------------------------------------------------------
