%-----------------------------------------------------------------------------%
% Letter class
\documentclass[11pt]{letter}
\usepackage{hyperref}
\usepackage[backend=bibtex,style=verbose,doi=false,isbn=false,url=false]{biblatex}
% \addbibresource{phd-bibliography/pollen-competition.bib}
\usepackage{geometry}
\geometry{textwidth=43em, textheight=52\baselineskip}
% Name of sender
\name{Alba Cervantes Loreto}
% Signature of sender
\signature{Alba Cervantes Loreto}
% Address of sender
\address
{
Alba Cervantes Loreto \\
 School of Biological Sciences\\
University of Canterbury, Christchurch 8140, New Zealand\\
albaricoque.cl.93@gmail.com\\
+64~22~508~6030
}
\date{05--Sept--2021}
%-----------------------------------------------------------------------------%
\begin{document}


% Name and address of receiver
\begin{letter}
{



    Tatauranga Aotearoa, Stats NZ\\
    Christchurch,\\
    New Zealand\\


}
% Opening statement
\opening{Dear Statistical Methods team, }
% Letter body
I am writing to apply for the Statistical and Data Analyst- Statistical methods position within Tatauranga Aotearoa, Stats NZ. Currently, I am about to finish my Ph.D. at the University of Canterbury, which is focused on analyzing ecological questions using statistical and computational tools. My expected submission date is in November 2021.


I am a computational ecologist, with more than 5 years of experience working in research. My years in science have given me a solid understanding of how to turn data into insights. I have extensive experience collecting, managing, cleaning, and wrangling datasets to meet the required standards for reproducible analyses. Furthermore, during my Ph.D., I specialized in implementing a range of modeling frameworks varying from linear models, bayesian mixed-effects models, and network analysis to understand how biodiversity is maintained in natural communities.  I believe I am an excellent candidate for this position because I have both the quantitative background and computational skills to meet the needs of advanced statistical analyses and data solutions required by the Design Work Stream. Particularly, given my background I believe I could make a positive contribution to the Environment and Economic Collections team.
%transform data into insights.


My skills are not only limited to the analytical aspect of science. I have a strong understanding of the importance of collaborative work and I have the proven ability to communicate complex findings in a variety of ways such as scientific papers, technical reports, and oral presentations. Furthermore, my teaching experience has proven my ability to guide and educate people in the process of analyzing data, which is an aspect of my career that I have particularly enjoyed. I have been part of many collaborations with different groups, and I genuinely enjoy working in a team. I also firmly believe the best outcomes are achieved when people within different disciplines work together. I am convinced that my excellent interpersonal skills will allow me to adapt and positively contribute to The Design Work Stream .


 %Finally, being involved in ecological research has fueled my curiosity in finding new ways of analyzing data, as well as the ability to constantly learn new skills. This passion

After years in academia, I am ready for a change. I have decided to pursue my passion for public service to contribute my gained skills, experience, and commitment to the country that I now call home, Aotearoa New Zealand. Tatauranga Aotearoa, Stats NZ offers an exciting opportunity to do so, as it is an interdisciplinary agency focused on improving the wellbeing of the people of this country. Furthermore, as a scientist, I realize the value of data not only to tell stories but as a guide into how the future could look like. I believe Tatauranga Aotearoa, Stats NZ shares that vision. I feel equipped to respond to the challenges offered by this position, please let me know if I can provide additional information to aid you in the evaluation of my application. Thank you for considering my application, and I look forward to hearing from you.
\vfill

\hfill
Alba Cervantes Loreto

\medskip
% Closing statement
% \closing{ }
\end{letter}
\end{document}
%-----------------------------------------------------------------------------
